---
title: "Reddit Question - Aggregation"
author: "thaufas"
date: "10/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## Overview
**Source**: [Reddit.com/r/Rlanguage | Noob question: how do I combine data? ](https://www.reddit.com/r/Rlanguage/comments/q54d0k/noob_question_how_do_i_combine_data/)

### Step 1: Build a Data Set for Testing

```{r BuildDataSet}

library(tibble)

numRows <- 30
careerChoiceRanks <- c("1st", "2nd", "3rd+", "Others")
set.seed(2^8 + 3)

ds1 <- tibble(
  Job.Type = rep("Teacher", numRows),
  Industry.Type = rep("Education", numRows),
  Career.Choice.Rank = factor(
    x = sample(careerChoiceRanks, numRows, TRUE),
    levels = careerChoiceRanks,
    labels = careerChoiceRanks,
    ordered = TRUE
  )
)

print(ds1)

```

### Step 2a: Use the `tidyverse::dplyr` package to create frequency tallies.

```{r ViewTallies}

library(dplyr)

ds1 %>%
  group_by_all() %>% 
  summarize(n = n())

```

### Step 2b: Use the `kableExtra` package to display the tables in an HTML-friendly manner. (Optional)

In this step, the use of the `kableExtra` package's `kable()` function is completely optional and should only be used if you need/want to display the results in a web-page, RNotebook, Jupyter notebook, *etc.*

Also, note that I was able to perform all of the following operations by using the `%>%` operator to create a pipeline by *chaining* the output of the previous operation as input to the next operation.

1. Process the `ds1` data frame to show tallies and pass it to the `kableExtra()` function.

1. Use the `kableExtra()` function to generate HTML output suitable for display in a webpage, then pass the output of the `kableExtra()` function.

1. Use the `kable_styling()` function to apply style elements to the resulting HTML table to make it *responsive* in a UI sense and to make it more pleasing in appearance by adding borders and alternating colors.

Note that the first 3 lines of the workflow shown here are exactly the same as shown above in **Step 2a**, with one exception: the terminal `%>%` operator. Here, the terminal `%>%` operator is used to feed the resulting data frame (which, technically speaking is actually a tibble) to the `kableExtra()` function.

This ability to *chain* together operations and build up a pipeline one step at a time is one of the most powerful aspects of using the `tidyverse` for building modern data science pipelines.

```{r ViewDataAsHTML}
library(kableExtra)

ds1 %>%
  group_by_all() %>%                          # Tell dplyr which variables to use for grouping
  summarize(n = n()) %>%                      # Compute the tallies for each variable group
  kable() %>%                                 # Generate a table, which can be HTML, LaTeX
  kable_styling(                              # Style the HTML table
    bootstrap_options = c(                    # Pass in the options to be used by the Bootstrap framework
      "striped"                               #    - Color each alternating row differently
      ,"condensed"                            #    - Remove unnecessary space
      ,"bordered"                             #    - Add line borders to all cells
      ,"hover"                                #    - Change active cell color focus on hover
    )
  )

```




### Step 3: Use the `tidyverse::ggplot2` package to plot the results.
```{r PlotFreq}

library(ggplot2)
library(scales)

p1 <- ggplot(ds1, aes(x = Career.Choice.Rank, fill = Career.Choice.Rank)) +
  geom_bar(color = "black", show.legend = FALSE) +
  scale_fill_discrete() +
  scale_y_continuous(breaks = seq(0, max(table(ds1$Career.Choice.Rank)) + 5, 2)) +
  labs(
    title = "Frequencies vs. Career Choice Ranks",
    x = "Career Choice Rank",
    y = "Frequencies (counts)"
  )

print(p1)

```

<div style="margin-bottom: 5em;"></div>
