---
title: "Reddit - Generating a Frequency Table"
author: "thaufas"
date: "3/3/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

**Source**: <https://www.reddit.com/r/Rlanguage/comments/t61r9n/can_somebody_please_help_part_of_a_quality/>

## Option 1 - Using only `base R` Functions

### Pros

* Uses only `base R`

* Code is very simple to understand

### Cons

* Code is not rugged

```{r, eval=TRUE, echo=TRUE}
datFile <- "2022-03-03_010_100_Generate_Freq_Table_Data.txt"

dat2 <- as.numeric(readr::read_lines(datFile))

table(dat2)
```

## Option 2 - Using `tidyverse` Packages

### Pros

* Coding logic isn't as simple as that shown in Option 1, but it's still easy to understand

* This code is more rugged than what is shown in Option 1, which has multiple advantages.

   * The *pipeline* nature of the `tidyverse` enables easy extension of the code without worrying about breaking something.
   
   * If the code is modified, errors are more likely to be caught &emdash; even without writing explicit checks &mdash; because the `tidyverse` generally has *strong type checking*.

### Cons

* Requires installing packages to extend R's base functionality

```{r, eval=TRUE}
library(readr)
library(dplyr)

datFile <- "2022-03-03_010_100_Generate_Freq_Table_Data.txt"

dat1 <- readr::read_fwf(
  file = datFile,
  col_positions = readr::fwf_cols(vals = 4),
  col_types = cols(readr::col_double()),
  trim_ws = TRUE
)

dat2 <- dat1 |>
  group_by(vals) |> 
  summarise(n = n())
```

```{r, echo=FALSE}
library(kableExtra)

dat2 |>
  kableExtra::kbl() |> 
  kableExtra::kable_styling(
    bootstrap_options = c("bordered", "hover", "responsive", "striped"),
    full_width = FALSE
  )
```

## Data Files

The contents of the file named ```r datFile```, which contains the raw data, are shown here.

```{r, results = 'asis', echo=FALSE}
dat <- readLines(datFile)

cat(paste0("     ", dat, collapse = "\n"))
```

<div style="margin: 1em 0 5em 0">
</div>
